\documentclass{article}



\begin{document}



\begin{center} \textbf {I'M CRIS LOURENZ TAN A \\ FREELANCE SOFTWARE DEVELOPER} \end{center}



\section{Biography}



Hi, I'm Cris Lourenz Tan a freelance software developer based in Australia. Cris is a skilled software developer with 1 year of experience. He knows how to create computer programs that are easy to use and work well. Cris has worked on many different projects, from small phone apps to big computer systems. He knows how to use a lot of different programming languages and is always trying to learn more. Cris likes working with other people and is a good team player. He likes to play badminton, basketball, online video games, and many more. He also goes to meetings to learn about new things in the computer world. Cris is really good at what he does, and can help out the people who are in needs of help for their projects to be successful.





\section{Future Plans}



I'm looking forward to using the \textbf{knowledge} I gained in this class in a variety of projects in the future. \emph{Machine learning} and \emph{artificial intelligence} are two areas that particularly pique my interest. I accept that these advancements can possibly change the manner in which we approach various fields, from \textbf{medical services} to \textbf{fund to transportation}. Additionally, I'm interested in learning how these technologies can be applied to the development of environmentally friendly and more sustainable solutions, such as smarter energy grids or more effective transportation networks. Eventually, I desire to utilize the abilities I've mastered in this course to make creative answers for a portion of the world's most squeezing issues.





\subsection{Professional Conduct}



\textbf{Professional conduct} is a crucial aspect of working with modern computing resources such as \emph{virtual machines} and \emph{containers}.  These advancements are in many cases utilized in enormous scope creation conditions, where even little mix-ups can have critical results. Thusly, it's critical to move toward their creation, sending, and the executives with extreme attention to detail and tender loving care. This includes adhering to security best practices like ensuring that sensitive data is appropriately encrypted and protected and that only those who need it have access to resources. It also means following industry standards for scalability and reliability, like designing systems that can handle a lot of traffic and making sure there are backups and failover mechanisms in case something goes wrong without warning. We can contribute to ensuring that these technologies are utilized to their full potential while simultaneously reducing the likelihood of errors and other issues by placing professional conduct first when using them.



\subsection{Mathematics Section}

Here is the math related section:



\begin{equation}

y=x^+\sqrt{x}

\end{equation}



\begin{equation}

y=\sum_{n=0}^N n^2

\end{equation}



\begin{equation}

e=mc^2

\end{equation}





\subsection{Table Section}

Here is the table related section: \\



\begin{tabular}{|c|c|c|c|}

\hline

Component & Start Date & End Date & Lines of Code \\

\hline

Project 1 & 01/01/2021 & 31/03/2021 & 1000 \\

Project 2 & 01/04/2021 & 30/06/2021 & 2000 \\

Project 3 & 01/07/2021 & 30/09/2021 & 1500 \\

\hline

\end{tabular}



\end{document}
